Hybrid platforms and bargaining power

### 2024-05-26 src/paper/application.tex
Extra justification for pricing assumption

Finally, this assumption is not as unrealistic as it might seem at first.
For example, the platform might be producing its products through a number of subsidiaries, which are legally separate entities, thus having no control over operational decisions, but still getting the profits from the sales.
Alternatively, there might be some kind of internal competition between the different product teams, which would lead to a similar outcome.

>>>>

A number of other papers using the same demand system \parencite[e.g.][]{anderson2020aggregative,anderson2021hybrid} achieve essentially the same outcome by relying on the timing of the model.
Specifically, if the platform sets product prices before the fringe firms make their entry decisions, the aggregate demand will not depend on the platform's product prices\footnote{
    At least in the hybrid regime.
    The optimum in the pure retailer regime is somewhat different.
}.
This in turn means that the platform will optimally price its products as if they were produced by separate sellers.
In the current paper, such a timing would be problematic, because the aim is to keep the benchmark and bargaining models as similar as possible.
It would be unrealistic to assume that the platform can commit to prices before the fringe firms make their investment decisions, while at the same time it cannot commit to an entry fee in the latter model.

Finally, even taken at face value, this assumption about the platform's pricing is not as unrealistic as it might seem at first.
For example, the platform might be producing its products through a number of subsidiaries, which are legally separate entities, thus having no control over operational decisions, but still getting the profits from the sales.
Alternatively, there might be some kind of internal competition between the different product teams, which would lead to a similar outcome.
